---
title: "COMPULSIVE TESTING AND ACADEMIC FUNCTIONING"
author: "Diego Figueiras"
geometry: [top=1in, bottom=1in, right=1in, left=1in]
year: "2024"
degree: "PhD"
field: "Industrial/Organizational Psychology"
department: "Psychology"
uni: "Montclair State University"
location: "Montclair, NJ"
chair: "Michael Bixter"
committee2: "Kevin Askew"
committee3: "John Kulas"
gradschool: "Richard S. Inouye, Ph.D."
gradschoollabel: "Vice Provost for Graduate Studies"
bibliography: yourbibfile.bib
multipaper: true
output:
  dissertateUSU::dissertateUSU:
    latex_engine: xelatex
    keep_tex: yes
    pandoc_args: [ "--csl", "apa7.csl" ]
---

```{r global_options, include=FALSE}
## This saves you from having to do this for every chunk
knitr::opts_chunk$set(fig.path = 'figures/',
                      echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE)
library(dissertateUSU)
```

<!-- Abstract -->

\newpage

\pagestyle{plain} <!-- can use \pagestyle{fancy} for a horizontal line in header --> \fancyhead[R]{\thepage} \fancyfoot[C]{}

```{=tex}
\chapter*{ABSTRACT}
\addcontentsline{toc}{section}{Abstract}
```
```{=tex}
\abstracttitle
\doublespacing
```
Your abstract words go here. The line below puts the total number of pages at the end of your abstract (as required).

```{=tex}
\begin{flushright}(\pageref{LastPage} pages)\end{flushright}
```
<!-- Public Abstract -->

```{=tex}
\newpage
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\chapter*{PUBLIC ABSTRACT}
\addcontentsline{toc}{section}{Public Abstract}
\doublespacing
```
Your publicly abstracted words go here.

<!-- Dedication -->

```{=tex}
\newpage
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\chapter*{DEDICATION}
\addcontentsline{toc}{section}{Dedication}
```
Dedicate it.

<!-- Acknowledgments -->

```{=tex}
\newpage
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\chapter*{ACKNOWLEDGMENTS}
\addcontentsline{toc}{section}{Acknowledgments}
```
Acknowledge those acknowledgable individuals and things.

<!-- Front Matter -->

```{=tex}
\newpage
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\tableofcontents
```
```{=tex}
\newpage
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\listoftables
```
```{=tex}
\newpage
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
\listoffigures
```
```{=tex}
\newpage
\pagenumbering{arabic}
```
<!-- Chapter 1 -->

```{=tex}
\newpage
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
```
\chapter{INTRODUCTION}

```{r, child="Chapter1.Rmd"}
```

<!-- Chapter 2 -->

```{=tex}
\FloatBarrier
\newpage
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
```
\chapter{Chapter 2's Title}

```{r, child="Chapter2.Rmd"}
```

<!-- Chapter 3 -->

```{=tex}
\FloatBarrier
\newpage
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
```
\chapter{Chapter 3's Title}

```{r, child="Chapter3.Rmd"}
```

<!-- Chapter 4 -->

```{=tex}
\FloatBarrier
\newpage
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
```
\chapter{Chapter 4's Title}

```{r, child="Chapter4.Rmd"}
```

<!-- Chapter 5 -->

```{=tex}
\FloatBarrier
\newpage
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
```
\chapter{Chapter 5's Title}

```{r, child="Chapter5.Rmd"}
```

<!-- References -->

```{=tex}
\FloatBarrier
\newpage
\fancyhead[R]{\thepage}
\fancyfoot[C]{}
```
\chapter*{REFERENCES}

```{=tex}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.4in}
\setlength{\parskip}{6pt}
```
\noindent
